parental migration and adolescents educational performance

### 2022-06-10 data/Gu-thesis-script.Rmd
change dependent var measures; remove outliers

Load packages
```{r}
library(tidyverse) 
library(haven)
library(fixest)
library(modelsummary)
```

@@

Assemble a panel dataset in wide format
```{r}
d_1 <- d_stu1 %>% left_join(d_par1, by=c('ids', 'clsids', 'schids', 'ctyids', 'fall')) 
d_2 <- d_stu2 %>% left_join(d_par2, by=c('ids', 'clsids', 'w2clsids', 'schids', 'ctyids', 'w2fall'))
d <- d_1 %>% right_join(d_2, by=c('ids', 'clsids', 'schids', 'ctyids'))
```

```{r}
d <- d %>% mutate(
  age = 2013 - a02a, #student's age at baseline
  local.resi = age - a07 #years of residence at the current county
)
```

Compute standardized exam grades (within-school z-scores)
```{r}
d <- d %>% #Total exam grades at wave 1 and at wave 2
  mutate(w1ttl = tr_chn + tr_mat + tr_eng, 
         w2ttl = w2chn + w2mat + w2eng) 
d <- d %>% #Within-school z-scores for Chinese, math, English exams and their total, respectively
  group_by(schids) %>%
  mutate(w1chn_std = as.numeric(scale(tr_chn)),
         w1mat_std = as.numeric(scale(tr_mat)),
         w1eng_std = as.numeric(scale(tr_eng)),
         w1ttl_std = as.numeric(scale(w1ttl)),
         w2chn_std = as.numeric(scale(w2chn)),
         w2mat_std = as.numeric(scale(w2mat)),
         w2eng_std = as.numeric(scale(w2eng)),
         w2ttl_std = as.numeric(scale(w2ttl))
         ) %>% ungroup()
```

@@

## Variables 
Dependent variables: Outcome differences between wave 2 and wave 1
```{r}
d_cl <- d_cl %>% mutate(
  chn_std = w2chn_std - w1chn_std,
  mat_std = w2mat_std - w1mat_std,
  eng_std = w2eng_std - w1eng_std,
  ttl_std = w2ttl_std - w1ttl_std,
  cog = w2cog3pl - cog3pl 
) %>%
  drop_na(cog, chn_std, mat_std, eng_std, ttl_std)
```

@@

@@

### Wave 2 outcomes of treatment group vs control group
```{r}
d_cl %>%
  group_by(migr) %>% 
  summarise(n_cases = n(),
            mean_cog = mean(w2cog3pl, na.rm=T),
            mean_ttl = mean(w2ttl_std, na.rm=T),
            mean_chn = mean(w2chn_std, na.rm=T),
            mean_mat = mean(w2mat_std, na.rm=T),
            mean_eng = mean(w2eng_std, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(migr_mo_only) %>% 
  summarise(n_cases = n(),
            mean_cog = mean(w2cog3pl, na.rm=T),
            mean_ttl = mean(w2ttl_std, na.rm=T),
            mean_chn = mean(w2chn_std, na.rm=T),
            mean_mat = mean(w2mat_std, na.rm=T),
            mean_eng = mean(w2eng_std, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(migr_mo) %>% 
  summarise(n_cases = n(),
            mean_cog = mean(w2cog3pl, na.rm=T),
            mean_ttl = mean(w2ttl_std, na.rm=T),
            mean_chn = mean(w2chn_std, na.rm=T),
            mean_mat = mean(w2mat_std, na.rm=T),
            mean_eng = mean(w2eng_std, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(migr_fa_only) %>% 
  summarise(n_cases = n(),
            mean_cog = mean(w2cog3pl, na.rm=T),
            mean_ttl = mean(w2ttl_std, na.rm=T),
            mean_chn = mean(w2chn_std, na.rm=T),
            mean_mat = mean(w2mat_std, na.rm=T),
            mean_eng = mean(w2eng_std, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(migr_fa) %>% 
  summarise(n_cases = n(),
            mean_cog = mean(w2cog3pl, na.rm=T),
            mean_ttl = mean(w2ttl_std, na.rm=T),
            mean_chn = mean(w2chn_std, na.rm=T),
            mean_mat = mean(w2mat_std, na.rm=T),
            mean_eng = mean(w2eng_std, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(migr_both) %>% 
  summarise(n_cases = n(),
            mean_cog = mean(w2cog3pl, na.rm=T),
            mean_ttl = mean(w2ttl_std, na.rm=T),
            mean_chn = mean(w2chn_std, na.rm=T),
            mean_mat = mean(w2mat_std, na.rm=T),
            mean_eng = mean(w2eng_std, na.rm=T)
            ) %>%
  drop_na()
```

### Change in outcomes of treatment group vs control group
```{r}
d_cl %>%
  group_by(migr) %>% 
  summarise(n_cases = n(),
            mean_change_cog = mean(cog, na.rm=T),
            mean_change_ttl = mean(ttl_std, na.rm=T),
            mean_change_chn = mean(chn_std, na.rm=T),
            mean_change_mat = mean(mat_std, na.rm=T),
            mean_change_eng = mean(eng_std, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(migr_mo_only) %>% 
  summarise(n_cases = n(),
            mean_cog = mean(w2cog3pl, na.rm=T),
            mean_ttl = mean(w2ttl_std, na.rm=T),
            mean_chn = mean(w2chn_std, na.rm=T),
            mean_mat = mean(w2mat_std, na.rm=T),
            mean_eng = mean(w2eng_std, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(migr_mo) %>% 
  summarise(n_cases = n(),
            mean_change_cog = mean(cog, na.rm=T),
            mean_change_ttl = mean(ttl_std, na.rm=T),
            mean_change_chn = mean(chn_std, na.rm=T),
            mean_change_mat = mean(mat_std, na.rm=T),
            mean_change_eng = mean(eng_std, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(migr_fa_only) %>% 
  summarise(n_cases = n(),
            mean_change_cog = mean(cog, na.rm=T),
            mean_change_ttl = mean(ttl_std, na.rm=T),
            mean_change_chn = mean(chn_std, na.rm=T),
            mean_change_mat = mean(mat_std, na.rm=T),
            mean_change_eng = mean(eng_std, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(migr_fa) %>% 
  summarise(n_cases = n(),
            mean_change_cog = mean(cog, na.rm=T),
            mean_change_ttl = mean(ttl_std, na.rm=T),
            mean_change_chn = mean(chn_std, na.rm=T),
            mean_change_mat = mean(mat_std, na.rm=T),
            mean_change_eng = mean(eng_std, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(migr_both) %>% 
  summarise(n_cases = n(),
            mean_change_cog = mean(cog, na.rm=T),
            mean_change_ttl = mean(ttl_std, na.rm=T),
            mean_change_chn = mean(chn_std, na.rm=T),
            mean_change_mat = mean(mat_std, na.rm=T),
            mean_change_eng = mean(eng_std, na.rm=T)
            ) %>%
  drop_na()
```

## DID adjusted
$$\Delta score_{i,s} = \alpha + \beta \cdot migr_{i,s} + \gamma \cdot FE_{s} + \theta \cdot X_{i,s} + \varepsilon_{i,s}$$
$$X_{i,s}$$ denotes a vector of covariates about the characteristics of students, parents, and households.

Regressing on cognitive test score (standardized)
```{r}
did_adj_cog <- feols(cog ~ migr  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_cog_m_only <- feols(cog ~ migr_mo_only + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_cog_m <- feols(cog ~ migr_mo + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_cog_f_only <- feols(cog ~ migr_fa_only + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_cog_f <- feols(cog ~ migr_fa + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_cog_both <- feols(cog ~ migr_both + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
```

Results
```{r}
models_adj_cog <- list(
did_adj_cog,
did_adj_cog_m_only,
did_adj_cog_m,
did_adj_cog_f_only,
did_adj_cog_f,
did_adj_cog_both) 
models_adj_cog %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
```

Regressing on total exam score
```{r}
did_adj_ttl <- feols(ttl_std ~ migr + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_ttl_m_only <- feols(ttl_std ~ migr_mo_only + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_ttl_m <- feols(ttl_std ~ migr_mo + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_ttl_f <- feols(ttl_std ~ migr_fa + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_ttl_f_only <- feols(ttl_std ~ migr_fa_only + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_ttl_both <- feols(ttl_std ~ migr_both + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
```

Results
```{r}
models_adj_ttl <- list(
did_adj_ttl,
did_adj_ttl_m_only,
did_adj_ttl_m,
did_adj_ttl_f_only,
did_adj_ttl_f,
did_adj_ttl_both) 
models_adj_ttl %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
```

Regressing on Chinese exam score
```{r}
did_adj_chn <- feols(chn_std ~ migr + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_chn_m_only <- feols(chn_std ~ migr_mo_only + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_chn_m <- feols(chn_std ~ migr_mo + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_chn_f_only <- feols(chn_std ~ migr_fa_only + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_chn_f <- feols(chn_std ~ migr_fa + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_chn_both <- feols(chn_std ~ migr_both + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
```

Results
```{r}
models_adj_chn <- list(
did_adj_chn,
did_adj_chn_m_only,
did_adj_chn_m,
did_adj_chn_f_only,
did_adj_chn_f,
did_adj_chn_both) 
models_adj_chn %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
```

Regressing on Math score
```{r}
did_adj_mat <- feols(mat_std ~ migr + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_mat_m_only <- feols(mat_std ~ migr_mo_only + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_mat_m <- feols(mat_std ~ migr_mo + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_mat_f_only <- feols(mat_std ~ migr_fa_only + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_mat_f <- feols(mat_std ~ migr_fa + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_mat_both <- feols(mat_std ~ migr_both + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
```

Results
```{r}
models_adj_mat <- list(
did_adj_mat,
did_adj_mat_m_only,
did_adj_mat_m,
did_adj_mat_f_only,
did_adj_mat_f,
did_adj_mat_both) 
models_adj_mat %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
```

Regressing on English score
```{r}
did_adj_eng <- feols(eng_std ~ migr  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_eng_m <- feols(eng_std ~ migr_mo  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
did_adj_eng_m_only <- feols(eng_std ~ migr_mo_only  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_eng_f <- feols(eng_std ~ migr_fa  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_eng_f_only <- feols(eng_std ~ migr_fa_only  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_eng_both <- feols(eng_std ~ migr_both  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
```

Results
```{r}
models_adj_eng <- list(
did_adj_eng,
did_adj_eng_m_only,
did_adj_eng_m,
did_adj_eng_f_only,
did_adj_eng_f,
did_adj_eng_both) 
models_adj_eng %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
```

>>>>

Load packages
```{r}
library(tidyverse) 
library(haven)
library(fixest)
library(modelsummary)
library(MatchIt)
library(datawizard)
```

@@

Assemble a panel dataset in wide format
```{r}
dw1 <- d_stu1 %>% left_join(d_par1, by=c('ids', 'clsids', 'schids', 'ctyids', 'fall')) 
dw2 <- d_stu2 %>% left_join(d_par2, by=c('ids', 'clsids', 'w2clsids', 'schids', 'ctyids', 'w2fall'))
d <- dw1 %>% right_join(dw2, by=c('ids', 'clsids', 'schids', 'ctyids'))
```

```{r}
d <- d %>% mutate(
  age = 2013 - a02a, #student's age at baseline
  local.resi = age - a07, #years of residence at the current county
  w1chn_100 = tr_chn/w2upchn*100,
  w1mat_100 = tr_mat/w2upmat*100,
  w1eng_100 = tr_eng/w2upeng*100,
  w2chn_100 = w2chn/w2upchn*100,
  w2mat_100 = w2mat/w2upmat*100,
  w2eng_100 = w2eng/w2upeng*100
)
d <- d %>% mutate(
  w1ttl_100 = w1chn_100 + w1mat_100 + w1eng_100,
  w2ttl_100 = w2chn_100 + w2mat_100 + w2eng_100,
  )
```

```{r}
d_cl1 <- d_cl %>% anti_join(d_outlier, by=c('ids', 'clsids', 'schids', 'ctyids'))
```

Compute standardized exam grades (within-school z-scores)
```{r}
d <- d %>% #Within-school standardization for Chinese, math, English exams and their total, respectively
  group_by(schids) %>%
  mutate(w1chn_mean = mean(w1chn_100, na.rm=T),
         w1mat_mean = mean(w1mat_100, na.rm=T),
         w1eng_mean = mean(w1eng_100, na.rm=T),
         w1ttl_mean = mean(w1ttl_100, na.rm=T),
         w2chn_mean = mean(w2chn_100, na.rm=T),
         w2mat_mean = mean(w2mat_100, na.rm=T),
         w2eng_mean = mean(w2eng_100, na.rm=T),
         w2ttl_mean = mean(w2ttl_100, na.rm=T),
         )  %>% ungroup()
d <- d %>% 
  mutate(w1chn_dif = w1chn_100 - w1chn_mean,
         w1mat_dif = w1mat_100 - w1mat_mean,
         w1eng_dif = w1eng_100 - w1eng_mean,
         w1ttl_dif = w1ttl_100 - w1ttl_mean,
         w2chn_dif = w2chn_100 - w2chn_mean,
         w2mat_dif = w2mat_100 - w2mat_mean,
         w2eng_dif = w2eng_100 - w2eng_mean,
         w2ttl_dif = w2ttl_100 - w2ttl_mean,
         cog_dif = w2cog3pl - cog3pl
         )
```

@@

## Variables 
```{r}
d_cl <- d_cl %>% 
  mutate(chn_dif = w2chn_dif - w1chn_dif,
         mat_dif = w2mat_dif - w1mat_dif,
         eng_dif = w2eng_dif - w1eng_dif,
         ttl_dif = w2ttl_dif - w1ttl_dif) %>%
  drop_na(cog_dif, chn_dif, mat_dif, eng_dif, ttl_dif)
```

@@

```
df <- d_cl %>% select(
  migr, migr_fa_only, migr_fa, migr_mo_only, migr_mo, migr_both,
  cog3pl, w1chn_dif, w1mat_std, w1eng_std,
  cog, chn_std, mat_dif, eng_dif,
  age, ch.girl, ch.health, ch.rural, ch.sibling, ch.boarding, ch.ethn.minority, 
  par.edu.year, home.book, home.internet
)
```

t-test
```{r}
t.test(cog_dif ~ migr, data = d_cl1)
t.test(ttl_dif ~ migr, data = d_cl1)
t.test(chn_dif ~ migr, data = d_cl1)
t.test(mat_dif ~ migr, data = d_cl1)
t.test(eng_dif ~ migr, data = d_cl1)
```

@@

### Wave 2 outcomes of treatment group vs control group
```{r}
d_cl %>%
  group_by(migr) %>% 
  summarise(n_cases = n(),
            mean_cog = mean(w2cog3pl, na.rm=T),
            mean_ttl = mean(w2ttl_dif, na.rm=T),
            mean_chn = mean(w2chn_dif, na.rm=T),
            mean_mat = mean(w2mat_dif, na.rm=T),
            mean_eng = mean(w2eng_dif, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(migr_mo_only) %>% 
  summarise(n_cases = n(),
            mean_cog = mean(w2cog3pl, na.rm=T),
            mean_ttl = mean(w2ttl_dif, na.rm=T),
            mean_chn = mean(w2chn_dif, na.rm=T),
            mean_mat = mean(w2mat_dif, na.rm=T),
            mean_eng = mean(w2eng_dif, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(migr_mo) %>% 
  summarise(n_cases = n(),
            mean_cog = mean(w2cog3pl, na.rm=T),
            mean_ttl = mean(w2ttl_dif, na.rm=T),
            mean_chn = mean(w2chn_dif, na.rm=T),
            mean_mat = mean(w2mat_dif, na.rm=T),
            mean_eng = mean(w2eng_dif, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(migr_fa_only) %>% 
  summarise(n_cases = n(),
            mean_cog = mean(w2cog3pl, na.rm=T),
            mean_ttl = mean(w2ttl_dif, na.rm=T),
            mean_chn = mean(w2chn_dif, na.rm=T),
            mean_mat = mean(w2mat_dif, na.rm=T),
            mean_eng = mean(w2eng_dif, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(migr_fa) %>% 
  summarise(n_cases = n(),
            mean_cog = mean(w2cog3pl, na.rm=T),
            mean_ttl = mean(w2ttl_dif, na.rm=T),
            mean_chn = mean(w2chn_dif, na.rm=T),
            mean_mat = mean(w2mat_dif, na.rm=T),
            mean_eng = mean(w2eng_dif, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(migr_both) %>% 
  summarise(n_cases = n(),
            mean_cog = mean(w2cog3pl, na.rm=T),
            mean_ttl = mean(w2ttl_dif, na.rm=T),
            mean_chn = mean(w2chn_dif, na.rm=T),
            mean_mat = mean(w2mat_dif, na.rm=T),
            mean_eng = mean(w2eng_dif, na.rm=T)
            ) %>%
  drop_na()
```

### Change in outcomes of treatment group vs control group
```{r}
d_cl %>%
  group_by(migr) %>% 
  summarise(n_cases = n(),
            mean_change_cog = mean(cog_dif, na.rm=T),
            mean_change_ttl = mean(ttl_dif, na.rm=T),
            mean_change_chn = mean(chn_dif, na.rm=T),
            mean_change_mat = mean(mat_dif, na.rm=T),
            mean_change_eng = mean(eng_dif, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(migr_mo_only) %>% 
  summarise(n_cases = n(),
            mean_change_cog = mean(cog_dif, na.rm=T),
            mean_change_ttl = mean(ttl_dif, na.rm=T),
            mean_change_chn = mean(chn_dif, na.rm=T),
            mean_change_mat = mean(mat_dif, na.rm=T),
            mean_change_eng = mean(eng_dif, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(migr_mo) %>% 
  summarise(n_cases = n(),
            mean_change_cog = mean(cog_dif, na.rm=T),
            mean_change_ttl = mean(ttl_dif, na.rm=T),
            mean_change_chn = mean(chn_dif, na.rm=T),
            mean_change_mat = mean(mat_dif, na.rm=T),
            mean_change_eng = mean(eng_dif, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(migr_fa_only) %>% 
  summarise(n_cases = n(),
            mean_change_cog = mean(cog_dif, na.rm=T),
            mean_change_ttl = mean(ttl_dif, na.rm=T),
            mean_change_chn = mean(chn_dif, na.rm=T),
            mean_change_mat = mean(mat_dif, na.rm=T),
            mean_change_eng = mean(eng_dif, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(migr_fa) %>% 
  summarise(n_cases = n(),
            mean_change_cog = mean(cog_dif, na.rm=T),
            mean_change_ttl = mean(ttl_dif, na.rm=T),
            mean_change_chn = mean(chn_dif, na.rm=T),
            mean_change_mat = mean(mat_dif, na.rm=T),
            mean_change_eng = mean(eng_dif, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(migr_both) %>% 
  summarise(n_cases = n(),
            mean_change_cog = mean(cog_dif, na.rm=T),
            mean_change_ttl = mean(ttl_dif, na.rm=T),
            mean_change_chn = mean(chn_dif, na.rm=T),
            mean_change_mat = mean(mat_dif, na.rm=T),
            mean_change_eng = mean(eng_dif, na.rm=T)
            ) %>%
  drop_na()
```

## DID unrestricted
Regressing on cognitive test score (standardized)
```{r}
did_unres_cog <- feols(cog_dif ~ migr + cog3pl | schids, data = d_cl1) 
did_unres_cog_m_only <- feols(cog_dif ~ migr_mo_only + cog3pl | schids, data = d_cl1) 
did_unres_cog_m <- feols(cog_dif ~ migr_mo + cog3pl | schids, data = d_cl1) 
did_unres_cog_f_only <- feols(cog_dif ~ migr_fa_only + cog3pl | schids, data = d_cl1) 
did_unres_cog_f <- feols(cog_dif ~ migr_fa + cog3pl | schids, data = d_cl1) 
did_unres_cog_both <- feols(cog_dif ~ migr_both + cog3pl | schids, data = d_cl1)
```

Results
```{r}
models_unres_cog <- list(
'Any Parent Absent' = did_unres_cog,
'Only Mother Absent' = did_unres_cog_m_only,
'Mother Absent' = did_unres_cog_m,
'Only Father Absent' = did_unres_cog_f_only,
'Father Absent' = did_unres_cog_f,
'Both Parents Absent' = did_unres_cog_both) 
table_unres_cog <- models_unres_cog %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
                              fmt = 2,
                              coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "cog3pl" = "Baseline Score"), output = 'markdown')
table_unres_cog
```

```{r}
did_unres_ttl <- feols(ttl_dif ~ migr + w1ttl_dif | schids, data = d_cl1) 
did_unres_ttl_m_only <- feols(ttl_dif ~ migr_mo_only + w1ttl_dif | schids, data = d_cl1) 
did_unres_ttl_m <- feols(ttl_dif ~ migr_mo + w1ttl_dif | schids, data = d_cl1) 
did_unres_ttl_f_only <- feols(ttl_dif ~ migr_fa_only + w1ttl_dif | schids, data = d_cl1) 
did_unres_ttl_f <- feols(ttl_dif ~ migr_fa + w1ttl_dif | schids, data = d_cl1) 
did_unres_ttl_both <- feols(ttl_dif ~ migr_both + w1ttl_dif | schids, data = d_cl1)
```

```{r}
models_unres_ttl <- list(
'Any Parent Absent' = did_unres_ttl,
'Only Mother Absent' = did_unres_ttl_m_only,
'Mother Absent' = did_unres_ttl_m,
'Only Father Absent' = did_unres_ttl_f_only,
'Father Absent' = did_unres_ttl_f,
'Both Parents Absent' = did_unres_ttl_both) 
table_unres_ttl <- models_unres_ttl %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
                              fmt = 2,
                              coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1ttl_dif" = "Baseline difference"), output = 'markdown')
table_unres_ttl
```

Regressing on Chinese exam score
```{r}
did_unres_chn <- feols(chn_dif ~ migr + w1chn_dif | schids, data = d_cl1) 
did_unres_chn_m_only <- feols(chn_dif ~ migr_mo_only + w1chn_dif | schids, data = d_cl1) 
did_unres_chn_m <- feols(chn_dif ~ migr_mo + w1chn_dif | schids, data = d_cl1) 
did_unres_chn_f_only <- feols(chn_dif ~ migr_fa_only + w1chn_dif | schids, data = d_cl1) 
did_unres_chn_f <- feols(chn_dif ~ migr_fa + w1chn_dif | schids, data = d_cl1) 
did_unres_chn_both <- feols(chn_dif ~ migr_both + w1chn_dif | schids, data = d_cl1)
```

Results
```{r}
models_unres_chn <- list(
'Any Parent Absent' = did_unres_chn,
'Only Mother Absent' = did_unres_chn_m_only,
'Mother Absent' = did_unres_chn_m,
'Only Father Absent' = did_unres_chn_f_only,
'Father Absent' = did_unres_chn_f,
'Both Parents Absent' = did_unres_chn_both) 
table_unres_chn <- models_unres_chn %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
                              fmt = 2,
                              coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1chn_dif" = "Baseline difference"), output = 'markdown')
table_unres_chn
```

Regressing on Math score
```{r}
did_unres_mat <- feols(mat_dif ~ migr + w1mat_dif| schids, data = d_cl1) 
did_unres_mat_m_only <- feols(mat_dif ~ migr_mo_only + w1mat_dif| schids, data = d_cl1) 
did_unres_mat_m <- feols(mat_dif ~ migr_mo + w1mat_dif| schids, data = d_cl1) 
did_unres_mat_f_only <- feols(mat_dif ~ migr_fa_only + w1mat_dif| schids, data = d_cl1) 
did_unres_mat_f <- feols(mat_dif ~ migr_fa + w1mat_dif| schids, data = d_cl1) 
did_unres_mat_both <- feols(mat_dif ~ migr_both + w1mat_dif| schids, data = d_cl1)
```

Results
```{r}
models_unres_mat <- list(
'Any Parent Absent' = did_unres_mat,
'Only Mother Absent' = did_unres_mat_m_only,
'Mother Absent' = did_unres_mat_m,
'Only Father Absent' = did_unres_mat_f_only,
'Father Absent' = did_unres_mat_f,
'Both Parents Absent' = did_unres_mat_both) 
table_unres_mat <- models_unres_mat %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
                              fmt = 2,
                              coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1mat_dif" = "Baseline Score"), output = 'markdown')
table_unres_mat
```

Regressing on English score
```{r}
did_unres_eng <- feols(eng_dif ~ migr + w1eng_dif| schids, data = d_cl1) 
did_unres_eng_m <- feols(eng_dif ~ migr_mo + w1eng_dif| schids, data = d_cl1)
did_unres_eng_m_only <- feols(eng_dif ~ migr_mo_only + w1eng_dif| schids, data = d_cl1) 
did_unres_eng_f <- feols(eng_dif ~ migr_fa + w1eng_dif| schids, data = d_cl1) 
did_unres_eng_f_only <- feols(eng_dif ~ migr_fa_only + w1eng_dif| schids, data = d_cl1) 
did_unres_eng_both <- feols(eng_dif ~ migr_both + w1eng_dif| schids, data = d_cl1)
```

Results
```{r}
models_unres_eng <- list(
'Any Parent Absent' = did_unres_eng,
'Only Mother Absent' = did_unres_eng_m_only,
'Mother Absent' = did_unres_eng_m,
'Only Father Absent' = did_unres_eng_f_only,
'Father Absent' = did_unres_eng_f,
'Both Parents Absent' = did_unres_eng_both) 
table_unres_eng <- models_unres_eng %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
                              fmt = 2,
                              coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1eng_dif" = "Baseline difference"), output = 'markdown')
table_unres_eng
```
